---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Bradford Dykes"
date: "8/26/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
#There are total 3 columns and 142 obs in the dino dataset


### Exercise 2
#The shape looks like dinosuar, and the correlation rate is 0.06447

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

# the shape looks like a star, and the correlation rate is about 0.06296 which is lower than the exercise 2
```{r}
star_data <- datasaurus_dozen %>% 
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
```{r}
star_data %>%
summarize(r = cor(x, y))
 ```
```

###Exercise 4
# The shape looks like a circle, and it has a higher correlation rate than dino which is about 0.0683
```{r}
circle_data <- datasaurus_dozen %>% 
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
circle_data  %>%
summarize(r = cor(x, y))
```

###Exercise 5
```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```